ME780 Assignment 1

### 2016-02-12 homework/homework_1/report.tex
Update report

\begin{align*}
	\mu_{0} &= 
		\begin{bmatrix}
			0 \\
			0 \\
			0
		\end{bmatrix} \\
	u_{0} &= 
	\begin{bmatrix}
		-15.5 \\
		-10.5 \\
		1.5
	\end{bmatrix} \\
	H_{t} &=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix} \\
	G_{t} 
		&= \begin{bmatrix}
			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
			0 & 0 & 1
		\end{bmatrix} \\
	    &= 
	        \begin{bmatrix}
		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
		        0 & 0 & 1
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            0 & 1 & l \\
	          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
	        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            r & 0 & 0 \\
	            0 & r & 0 \\
	            0 & 0 & r
	        \end{bmatrix}
		    \begin{bmatrix}
		       \omega_{1} \\
		       \omega_{2} \\
		       \omega_{3} \\
		    \end{bmatrix} \\
\end{align*}

>>>>

\begin{align*}
	\mu_{0} &= 
		\begin{bmatrix}
			0 \\
			0 \\
			0
		\end{bmatrix} \\
	u_{0} &= 
	\begin{bmatrix}
		-15.5 \\
		-10.5 \\
		1.5
	\end{bmatrix} \\
	H_{t} &=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix} \\
	G_{t} 
		&= \begin{bmatrix}
			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
			0 & 0 & 1
		\end{bmatrix} \\
	    &= 
	        \begin{bmatrix}
       			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
       			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
       			0 & 0 & 1
	        \end{bmatrix}^{-1}
	        A \\
	A_{t}
		&= J_{1}^{-1} J_{2} \omega \\		
		&=
			\begin{bmatrix}
				0 & 1 & l \\
				-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
				\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
			\end{bmatrix}^{-1}
			\begin{bmatrix}
				r & 0 & 0 \\
				0 & r & 0 \\
				0 & 0 & r
			\end{bmatrix}
			\begin{bmatrix}
				\omega_{1} \\
				\omega_{2} \\
				\omega_{3} \\
			\end{bmatrix} \\
\end{align*}

\newpage
\section{Adding GPS corrections to the EKF}

Previously it was assumed that the GPS and Magnetometer both work at a rate of 
10hz, however it is given that "corrections are sent for the x, y positions of 
the vechicle at an update rate of 1Hz. These corections improve the GPS 
measurements at that instance only, with an improved standard deviation of 
0.01m". This means that the measurement disturbance $Q$ changes over time (i.e. 
every 1Hz) from:

to (at every 1Hz):

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.1 & 0 & 0 \\
		0 & 0.1 & 0 \\
		0 & 0 & 0.1745		
	\end{bmatrix}
\end{equation}
